Conformance Checking Using Embeddings and their Applicability in the Internet of Things

### 2021-12-15 paper.tex
Fixes

\color{green}
The following paper is structured as follows.
First some background and important concepts for the rest of the paper are introduced n \cref{sec:background}.
This includes a deeper look the conformance checking problem, which is given in \cref{sub:conformance}, including a description of the two established families of techniques.
Furthermore the important limitations of these two approaches are highlighted.
Then a brief overview over the required NLP techniques is given in \cref{sub:nlp}.
Provided with the basic knowledge concerning both conformance checking and NLP, the novel embedding based conformance checking approaches from \cite{PBWe20} are described in \cref{sec:method}.
After the techniques have been outlined a discussion of the results from their experiments follows in \cref{sec:results}.
\cref{sec:discussion} concludes the paper with a consideration of limitations in their approach and possible future work, as well as a discussion of the applicability of these techniques in the Internet of Things.
\color{black}

\section{Background}
\label{sec:background}
\color{green}
Naturally there are numerous sub problems to be solved in business process management.
Often each problem can be viewed as a building block in a bigger system, and good solutions to one problem can enable more insightful further analyses in dependent problems.
For example the first step in many business process management use cases will be the discovery of a process model.
Once a process model has been obtained through some means further analyses can follow.
One of these fields is conformance checking, which as a technique, closely follows discovery, since it's main goal is to quantify how well a model conforms to a log.
There are currently two dominant branches of conformance checking, replay based algorithms and trace alignment algorithms.
Peeperkorn et al. present a novel conformance checking technique that follows and alternate route \cite{PBWe20} to address the conformance checking problem, through techniques adapted from natural language processing.
However, before this technique can be discussed in depth it is paramount to understand some of the basic ideas underlying both conformance checking and natural language processing. 
\color{black}

@@

\color{blue}
\begin{algorithm}
	\caption{Word Mover's distance}\label{alg:wmd}
	\begin{algorithmic}
		\State $n:=$ vocabulary size
		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
		\Function{$F_{WMD}$}{$p,q,c$}
			\State distance $\gets$ $\min \sum_{i,j=1}^n T_{ij}c(i,j)$
			\State subject to:
			\State $\sum_{j=1}^{n}T_{ij}=p_i \forall i \in \{1,...,n\}$ \Comment{Outflow}
			\State $\sum_{i=1}^{n}T_{ij}=q_j \forall j \in \{1,...,n\}$ \Comment{Inflow}
			\Return distance
		\EndFunction
	\end{algorithmic}
\end{algorithm}
The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
This family of metrics has proved itself to be quite robust as well as accurate in the past.
The Earth Mover's distance measures the distance between two probability distributions.
The informal interpretation of this is that there are two distributions, represented by piles of earth.
The distance between two distributions can be interpreted as the amount of work that needs to be done to transform one into the other.
Clearly, the work and thus the distance between two distributions depends on both the amount of earth on each of the piles and on the distance between piles.
Formally the EMD defines a distance metric for probability distributions over some vector space with a notion of distance.

@@

\subsubsection{Iterative Constrained Transfers}
\begin{algorithm}
	\caption{ACT}\label{alg:act}
	\begin{algorithmic}
		\State $k:=$ number of edges considered per activity
		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
		\State $h_p,h_q :=$ amount of different activities in trace $p$ and trace $q$ 
		\Function{$F_{ICT}$}{$p,q,c,k$}
		\For{$i=1...h_p$}
			\State $s \gets \arg \min_k(c(i,[1,...,h_q]))$ \Comment{Find $k$ activities with the smallest cost}
			\While{$l < k$}
				\State $r \gets \min(p_i,q_{s(l)}))$ \Comment{Edge constraint, move as much as possible but no more than allowed}
				\State $p_i \gets p_i - r$ \Comment{Move weight}
				\State $t \gets t + rc(i,j)$ \Comment{Update cost}
				\State $l \gets l+1$
			\EndWhile
			\If{$p_i \neq 0$} \Comment{Move any remaining weight in $p_i$ to $q_{s(k)}$}
				$t \gets t + p_ic(i,s(k))$ \Comment{Move rest to $q_{s(k)}$}
			\EndIf
		\EndFor
		\Return $t$
		\EndFunction
	\end{algorithmic}
\end{algorithm}
The EMD and variants of it are very attractive since they are both very general and exhibit good accuracy for both search and classification.
A major drawback of such methods however is the cubic complexity in the size of the input distributions, which makes it infeasible for larger problems.
In the case of conformance checking the size of the input, distribution is determined by the number of activities in the log, for which good scalability is desired.
There are a number of techniques that aim to reduce the complexity of EMD-based approaches, that obtain an approximation of the EMD by relaxing some of the constraints.  
One example of such a method is the Relaxed Word Mover's distance which drops the second (inflow) constraint, thus greatly simplifying the solution.
While this makes it easier to calculate the solution, the RWMD only gives a lower bound on the WMD.
Another such method is the Iterative Constrained Transfers \cite{AtMi18} algorithm that has linear complexity in the size of the input distribution.
Instead of just dropping the inflow constraint it is instead replaced by an edge capacity constraint.
The main benefit of this is that it avoids the formulation as a linear program and is instead solvable using a much less powerful, but much quicker, direct algorithm.

>>>>

\color{red}
The following paper is structured as follows.
First some background and important concepts for the rest of the paper are introduced n \cref{sec:background}.
This includes a deeper look the conformance checking problem, which is given in \cref{sub:conformance}, including a description of the two established families of techniques.
Furthermore the important limitations of these two approaches are highlighted.
Then a brief overview over the required NLP techniques is given in \cref{sub:nlp}.
Provided with the basic knowledge concerning both conformance checking and NLP, the novel embedding based conformance checking approaches from \cite{PBWe20} are described in \cref{sec:method}.
After the techniques have been outlined a discussion of the results from their experiments follows in \cref{sec:results}.
\cref{sec:discussion} concludes the paper with a consideration of limitations in their approach and possible future work, as well as a discussion of the applicability of these techniques in the Internet of Things.
\color{black}

\section{Background}
\label{sec:background}
\color{red}
Naturally there are numerous sub problems to be solved in business process management.
Often each problem can be viewed as a building block in a bigger system, and good solutions to one problem can enable more insightful further analyses in dependent problems.
For example the first step in many business process management use cases will be the discovery of a process model.
Once a process model has been obtained through some means further analyses can follow.
One of these fields is conformance checking, which as a technique, closely follows discovery, since it's main goal is to quantify how well a model conforms to a log.
There are currently two dominant branches of conformance checking, replay based algorithms and trace alignment algorithms.
Peeperkorn et al. present a novel conformance checking technique that follows and alternate route \cite{PBWe20} to address the conformance checking problem, through techniques adapted from natural language processing.
However, before this technique can be discussed in depth it is paramount to understand some of the basic ideas underlying both conformance checking and natural language processing. 
\color{black}

@@

\color{blue}
\begin{algorithm}
	\caption{Word Mover's distance}\label{alg:wmd}
	\begin{algorithmic}
		\State $n:=$ vocabulary size
		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
		\Function{$F_{WMD}$}{$p,q,c$}
			\State distance $\gets$ $\min \sum_{i,j=1}^n T_{ij}c(i,j)$
			\State subject to:
			\State $\sum_{j=1}^{n}T_{ij}=p_i \forall i \in \{1,...,n\}$ \Comment{Outflow}
			\State $\sum_{i=1}^{n}T_{ij}=q_j \forall j \in \{1,...,n\}$ \Comment{Inflow}
			\State \Return distance
		\EndFunction
	\end{algorithmic}
\end{algorithm}
The Word Mover's Distance \cite{KSKW15} is a variant of the Earth Mover's Distance \cite{RTGu98} adapted for natural language processing.
This family of metrics has proved itself to be quite robust as well as accurate in the past.
The Earth Mover's distance measures the distance between two probability distributions.
The informal interpretation of this is that there are two distributions, represented by piles of earth.
The distance between two distributions can be interpreted as the amount of work that needs to be done to transform one into the other.
Clearly, the work and thus the distance between two distributions depends on both the amount of earth on each of the piles and on the distance between piles.
Formally the EMD defines a distance metric for probability distributions over some vector space with a notion of distance.

@@

\subsubsection{Iterative Constrained Transfers}
\begin{algorithm}
	\caption{ACT}\label{alg:act}
	\begin{algorithmic}
		\State $k:=$ number of edges considered per activity
		\State $p_i,q_i := $ normalized count of activity $i$ in $p$ or $q$ respectively
		\State $c(i,j) :=$ Distance between embeddings of activity $i$ and $j$
		\State $h_p,h_q :=$ amount of different activities in trace $p$ and trace $q$ 
		\Function{$F_{ICT}$}{$p,q,c,k$}
		\For{$i=1...h_p$}
			\State $s \gets \arg \min_k(c(i,[1,...,h_q]))$ \Comment{Find $k$ activities with the smallest cost}
			\While{$l < k$}
				\State $r \gets \min(p_i,q_{s(l)}))$ \Comment{Edge constraint, move as much as possible but no more than allowed}
				\State $p_i \gets p_i - r$ \Comment{Move weight}
				\State $t \gets t + rc(i,j)$ \Comment{Update cost}
				\State $l \gets l+1$
			\EndWhile
			\If{$p_i \neq 0$} \Comment{Move any remaining weight in $p_i$ to $q_{s(k)}$}
				\State $t \gets t + p_ic(i,s(k))$ \Comment{Move rest to $q_{s(k)}$}
			\EndIf
		\EndFor
		\State \Return $t$
		\EndFunction
	\end{algorithmic}
\end{algorithm}
The EMD and variants of it are very attractive since they are both very general and exhibit good accuracy for both search and classification.
A major drawback of such methods however is the cubic complexity in the size of the input distributions, which makes it infeasible for larger problems.
In the case of conformance checking the size of the input, distribution is determined by the number of activities in the log, for which good scalability is desired.
There are a number of techniques that aim to reduce the complexity of EMD-based approaches, that obtain an approximation of the EMD by relaxing some of the constraints.  
One example of such a method is the Relaxed Word Mover's distance which drops the second (inflow) constraint, thus greatly simplifying the solution.
While this makes it easier to calculate the solution, the RWMD only gives a lower bound on the WMD.
Another such method is the Iterative Constrained Transfers \cite{AtMi18} algorithm that has linear complexity in the size of the input distribution.
Instead of just dropping the inflow constraint it is instead replaced by an edge capacity constraint.
The main benefit of this is that it avoids the formulation as a linear program and is instead solvable using a much less powerful, but much quicker, direct algorithm.
